Deep mutational scanning of hemagglutinin helps distinguish the evolutionary fates of human H3N2 influenza virus lineages

### 2018-01-29 paper/manuscript.tex
Add author contributions and conflict of interest statement
Started adding methods for phylogenetic tree.

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{Please provide details of author contributions here.}
\authordeclaration{Please declare any conflict of interest here.}
\equalauthors{\textsuperscript{1}J.M.L. and J.H. contributed equally to this work.}
\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed: trevor@bedford.io, jbloom@fredhutch.org}

@@

\subsection*{Inference of human H3N2 phylogenetic tree}
\comment{John to add methods here. We downloaded X sequences from the Influenza Virus Resource ?.... etc. subsampled how? inferred the tree, ancestral state reconstruction, visualized the tree...}
To parse trunk mutations from side branch mutations, we defined a set of recent nodes sampled on or after Jan-1-2017, and traced these nodes back to their most recent common ancestor. 
We defined all branches ancestral to this most recent common ancestor as the trunk.
All nodes that do not have descendants isolated after 2017 were defined as side branch nodes.
Nodes descended from the most recent common ancestor were defined as unresolved, as it is still unclear whether these nodes will ultimately be on the trunk or side branches.
The phylogenetic tree is available as a JSON file on \comment{link to repository}.

>>>>

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{J.M.L. performed the experiments; J.M.L. and J.H. analyzed data with input from T.B. and J.D.B.; J.M.L. and J.D.B. wrote the paper with input from J.H. and T.B.; all authors designed and planned the project}
\authordeclaration{The authors declare no conflict of interest.}
\equalauthors{\textsuperscript{1}J.M.L. and J.H. contributed equally to this work.}
\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed: trevor@bedford.io, jbloom@fredhutch.org}

@@

\subsection*{Inference of human H3N2 phylogenetic tree}
We downloaded H3N2 HA sequences from 1968 to 2017 using a curated database of publicly available sequences from GISAID (https://github.com/nextstrain/fauna; commit 1281ed9).
We constructed an annotated phylogenetic tree from these sequences using Nextstrain's augur tool \cite{Hadfield224048} (https://github.com/nextstrain/augur; commit 006896d) with sequences subsampled to six viruses per month over the time interval of January 1, 1968 to April 1, 2017.
This subsampling selected 2,145 strains of H3N2's HA.
The tree was constructed with RAxML 8.2.10~\cite{stamatakis2006raxml}.
Ancestral state reconstruction and branch length timing were performed with treetime~\cite{Sagulenko2018}.

To parse trunk mutations from side branch mutations, we defined a set of recent nodes sampled on or after Jan-1-2017, and traced these nodes back to their most recent common ancestor.
We defined all branches ancestral to this most recent common ancestor as the trunk.
All nodes that do not have descendants isolated after 2017 were defined as side branch nodes.
Nodes descended from the most recent common ancestor were defined as unresolved, as it is still unclear whether these nodes will ultimately be on the trunk or side branches.
The phylogenetic tree is available as a JSON file on \comment{link to repository}.
